### 2019-12-02 thesis/txt/0-introduction.tex
fix decision tree graphic, remove list of listings, remove graphs for pretschner from introduction

This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
Chapter~\ref{sec:rw} also presents existing work on information extraction and retrieval techniques, as well as program synthesis from examples.
Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
It also introduces the three investigated techniques PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the comparison described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion-fw}.

Following we show selected plots from the study results section. RLR stands for the baseline technique \emph{Random Line Retrieval}:

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/success-partial-all.pdf}
		\caption{Success of chunk retrievals for all techniques}
		\label{fig:success-partial-all}
\end{figure}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Precision and recall of all techniques compared when training examples are in \emph{one} structural category}
		\label{fig:recall-precision-singlecategory-all}
\end{figure}

\begin{figure}[htbp]
		\centering
		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Precision and recall of all techniques compared when training examples are in \emph{more than one} structural categories}
		\label{fig:recall-precision-multicategory-all}
\end{figure}

>>>>

This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
Chapter~\ref{sec:rw} also presents existing work on information extraction and retrieval techniques, as well as program synthesis from examples.
Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
It also introduces the three investigated techniques PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the comparison described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion-fw}.%\\\\

% Following we show selected plots from the study results section. RLR stands for the baseline technique \emph{Random Line Retrieval}:

% \begin{figure}[htbp]
% 		\centering
% 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/success-partial-all.pdf}
% 		\caption{Success of chunk retrievals for all techniques}
% 		\label{fig:success-partial-all}
% \end{figure}

% \begin{figure}[htbp]
% 	\centering
% 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
% 		\caption{Precision and recall of all techniques compared when training examples are in \emph{one} structural category}
% 		\label{fig:recall-precision-singlecategory-all}
% \end{figure}

% \begin{figure}[htbp]
% 		\centering
% 		\includegraphics[width=0.75\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
% 		\caption{Precision and recall of all techniques compared when training examples are in \emph{more than one} structural categories}
% 		\label{fig:recall-precision-multicategory-all}
% \end{figure}
